### 2017-02-06 local-capability-machine.tex
notation in world theorem
Prove that malloc is safe to pass to an adversary.

@@

              \begin{specification}[Malloc v.2]
                \label{spec:malloc}
                $c_\malloc$ satisfies the specification for malloc iff
                \[  
                  \begin{aligned}
                    &c_\malloc = ((\entry,\glob),\_,\_,\_) \land\\
                    &\exists \iota_{\malloc,0} \ldotp \\
                    &\quad (\forall \iota' \futurestr \iota_{\malloc,0} \ldotp \forall W,i \ldotp W(i)=\iota' \Rightarrow \iota'.H (\iota'.s) (\xi^{-1}(W)) = \iota'.H (\iota'.s) (\xi^{-1}([i \mapsto W(i)])) ) \; \land \\
                    &\quad \iota_{\malloc,0}.v = \perma \; \land \\
                    &\quad (\forall \Phi \in \ExecConfs \ldotp \forall \ms_{\var{footprint}}, \hsframe \in \HeapSegments \ldotp \\
                    &\qquad \forall i, n, \size \in \nats \ldotp \forall
                    w_{\var{ret}} \in \Words \ldotp \\
                    &\qquad \quad \forall \iota_\malloc \futurestr \iota_{\malloc,0} \land \\
                    &\qquad \quad \memheap = \ms_{\var{footprint}} \uplus \hsframe \land \heapSat[\ms_{\var{footprint}}]{n}{[i \mapsto \iota_\malloc]} \land \\
                    &\qquad \quad \memreg(r_1) = \size \land \size \geq 0 \land  \memreg(r_0) = w_{\var{ret}} \land \\
                    &\qquad \quad \memreg(\pcreg) = \updatePcPerm{c_\malloc} \\ %and this needs to change with ABI.
                    &\qquad \quad \Rightarrow \\
                    &\qquad \qquad\exists \Phi' \in \ExecConfs \ldotp \exists \ms_{\var{footprint}}', \ms_{\var{alloc}} \in \HeapSegments\ldotp\\
                    &\qquad \qquad \quad \exists j \in \nats \ldotp \exists b',e'\in \Addrs \ldotp \exists \iota_\malloc' \in \Regions \ldotp \\
                    &\qquad \qquad \qquad \Phi \step[j] \Phi' \land \\
                    &\qquad \qquad \qquad \memheap[\Phi']=\ms_{\var{footprint}}' \uplus \hs_{\var{alloc}} \uplus \hsframe \land\\
                    &\qquad \qquad \qquad \iota_{\malloc}' \futurewk \iota_\malloc \land \\
                    &\qquad \qquad \qquad \heapSat[\ms_{\var{footprint}}']{n-j}{[i \mapsto \iota_\malloc']} \land \\
                    &\qquad \qquad \qquad \dom(\hs_{\var{alloc}}) = [b',e'] \land \forall a \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0  \land \\
                    &\qquad \qquad \qquad \memreg[\Phi'] = \memreg[\Phi]\update{\pcreg}{\updatePcPerm{w_{\var{ret}}}}\update{r_1}{((\rwx,\glob),b',e',b')} \land \\
                    &\qquad \qquad \qquad \size - 1 = e'-b' ) \land\\
                    &\quad (\forall \Phi \in \ExecConfs \ldotp (\memreg(r_1)
                    \not\in \ints \vee \memreg(r_1) < 0) \land \memreg(\pcreg) = \updatePcPerm{c_\malloc} \Rightarrow \exists j \in \nats \ldotp \Phi \step[j] \failed)
                  \end{aligned}
                \]
              \end{specification}
              In the specification above $\iota_\malloc'$ is a future region of the initial region that governs malloc.
              \lau{What about $c_\malloc$ and the value relation? Do we add this to the specification or try to prove it based on the specification?}

@@

        \item $\npair[n'-1]{c_\adv} \in \stdvr(W)$: for $n'' <
          n'-1$ and $W' \futurestr W$ show:
          \\$\npair[n'']{\updatePcPerm{c_\adv}} \in \stder(W')$.
          Use FTLR. \label{f1:adv}
        \end{enumproof}

@@

\begin{align*}
  & \writeCond{} : (\Regions \times \Globals) \fun \Worlds \monnefun \UPred{\Addrs^2}  \\
  & \writeCond{}(\iota,\gl)(W) =  \\
  & \quad \begin{aligned}[t]
    \{ \npair{(\start,\addrend)} \mid & \;\exists r \in \var{localityReg}(g,W) \ldotp \\
    & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
    & \;\qquad W(r)\nsupsim[n-1] \iota_{\start',\addrend'} \text{ and }\\
    & \;\qquad W(r) \text{ is address-stratified } \}
  \end{aligned}
\end{align*}

@@

\begin{lemma}[Malloc is safe to pass to adversary]
  \label{lem:malloc-in-vr}
  If $W(r) \futurestr \iota_{\malloc,0}$, then
  $\npair{c_\malloc} \in \stdvr(W)$ for all $n$.
\end{lemma}
\begin{proof}
  \begin{enumproof}
  \item $c_\malloc = ((\entry,\glob),\base,\addrend,\addr)$.\\
    By: the malloc specification (Specification~\ref{spec:malloc}).
  \item Suffices: $\npair{(\start,\addrend,\addr)}\in\entryCond{\glob}(W)$.\\
    By definition of $\stdvr(W)$.
  \item Assume: $n' < n$, $W'\futurestr W$.\\
    Suffices: $\npair[n']{((\exec,\glob),\start,\addrend,\addr)} \in
    \stder(W')$.\\
    By: definition of the $\entryCond{}$
  \item Assume: $n''\leq n'$,
    $\npair[n'']{\reg}\in\stdrr(W')$, $\heapSat[\ms]{n''}{W'}$\\
    Suffices:
    $\npair[n'']{(\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms)}\in\observations(W')$\\
    By: definition of $\stder(W')$
  \item Assume: $i < n''$,
    $(\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms\uplus\ms_f)\step[i]
    (\halted,\mem')$\\
    Suffices: $\exists W''\futurestr W',\ms_r,\ms'\ldotp$ $\mem' =
    \ms'\uplus\ms_r\uplus\ms_f$ and $\heapSat[\ms']{n-i}{W''}$\\
    By: definition of $\observations(W')$
  \item $W'(r) \futurestr \iota_{\malloc,0}$\\
    Easy from: $W'\futurestr W$ and $W(r) \futurestr \iota_{\malloc,0}$ using
    transitivity of $\futurestr$.
  \item $\exists P : \activeReg{W'} \rightarrow \HeapSegments \ldotp$
    $\memSatPar[n'']{\ms}{W'}{P}$, i.e. $\hs = \biguplus_{r\in\activeReg{W'}}P(r)$ and
    $\forall r \in \activeReg{W'} \ldotp$ $\exists H,s \ldotp$ $W'(r) =
    (\_,s,\_,\_,H)$ and $\npair[n'']{P(r)} \in H(s)(\xi^{-1}(W'))$\\
    By: definition of $\heapSat[\ms]{n''}{W'}$.
  \item Define $\ms_{\var{frame}} = \left(\biguplus_{r'\in\activeReg{W'},r'\neq
        r}P(r')\right)\uplus\ms_f$. Then $\ms\uplus\ms_f = P(r) \uplus
    \ms_{\var{frame}}$ and $\heapSat[P(r)]{n''}{W'(r).H~(W'(r).s)~(\xi^{-1}(W'))}$.
    Easy from the previous point.
  \item $\heapSat[P(r)]{n''}{W'(r).H~(W'(r).s)~(\xi^{-1}([r\mapsto W'(r)]))}$, i.e.
    $\heapSat[P(r)]{n''}{[r\mapsto W'(r)]}$.\\
    By: the malloc specification (Specification~\ref{spec:malloc}) from the
    previous point.
  \item Case: $\reg(r_1) \in \ints$ and $\reg(r_1) \geq 0$
    \begin{enumproof}
    \item Define $\var{size} = \reg(r_1)$
    \item $\exists \Phi' \in \ExecConfs, \ms_{\var{footprint}}',
      \ms_{\var{alloc}} \in \HeapSegments, j \in \nats, b',e'\in \Addrs,
      \iota_\malloc' \in \Regions \ldotp$
      $(\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms\uplus\ms_f)
      \step[j] \Phi'$ and $\memheap[\Phi']=\ms_{\var{footprint}}' \uplus
      \hs_{\var{alloc}} \uplus \ms_{\var{frame}}$ and $\iota_{\malloc}'
      \futurewk W'(r)$ and $\heapSat[\ms_{\var{footprint}}']{n-j}{[r \mapsto
        \iota_\malloc']}$ and $\dom(\hs_{\var{alloc}}) = [b',e']$ and $\forall a
      \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0$ and $\memreg[\Phi'] =
      \memreg[\Phi]\update{\pcreg}{\updatePcPerm{w_{\var{ret}}}}\update{r_1}{((\rwx,\glob),b',e',b')}$
      and $\var{size} - 1 = e'-b' )$.\\
      By: the malloc specification (Specification~\ref{spec:malloc}).
    \item Define $W'' = W'\update{r}{\iota_\malloc'}[i\mapsto
      \iota^\nwl_{b',e'}]$ for $i \not\in\dom(W')$
    \item \dominique{TODO}
    \end{enumproof}
  \item Case: $\reg(r_1)\not\in\ints \vee \reg(r_1) < 0$
    \begin{enumproof}
    \item $\exists j\ldotp (\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms\uplus\ms_f)\step[j]
      \failed$\\
      By: the malloc specification (Specification~\ref{spec:malloc}).
    \item Contradiction with 
      $(\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms\uplus\ms_f)\step[i]
      (\halted,\mem')$
    \end{enumproof}
  \end{enumproof}
\end{proof}

@@

\begin{lemma}[Transitivity proberties between private and public future worlds]
\[
  W'' \futurestr W' \land W' \futurewk W \Rightarrow W'' \futurestr W
\]
and
\[
  W'' \futurewk W' \land W' \futurestr W \Rightarrow W'' \futurestr W
\]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:future-priv-pub-trans}]
  % TODO
\end{proof}

@@

\subsubsection{Value relation}
\begin{lemma}[Value relation monotone wrt $\futurewk$]
  \label{lem:stdvr-mono-wk}
  \[
    W' \futurewk W \land \npair{w} \in \stdvr(W) \Rightarrow \npair{w} \in \stdvr(W')
  \]
\end{lemma}
\begin{proof}[Proof of lemma~\ref{lem:stdvr-mono-wk}]
  Follows from Lemma~\ref{lem:readcond-mono-pub}, Lemma~\ref{lem:writecond-mono-pub}, Lemma~\ref{lem:execcond-mono-pub}, and Lemma~\ref{lem:entrycond-mono-pub}.
\end{proof}

>>>>

\begin{lemma}[Determinacy]
  \label{lem:determinacy}
  If $\Phi \step \Phi'$ and $\Phi \step \Phi''$, then $\Phi' = \Phi''$.
  If $\Phi \step[n] \Phi'$ and $\Phi \step[n] \Phi''$, then $\Phi' = \Phi''$.
  If $\Phi \step[n] \Phi'$ and $\Phi \step[n'] (\halted,\mem'')$, then $n \geq n'$
  and $\Phi' \step[n'-n] (\halted,\mem'')$.
\end{lemma}
\begin{proof}
  By easy inspection of the definition of the operational semantics.
\end{proof}

@@

              \begin{specification}[Malloc v.2]
                \label{spec:malloc}
                $c_\malloc$ satisfies the specification for malloc iff
                \[  
                  \begin{aligned}
                    &c_\malloc = ((\entry,\glob),\_,\_,\_) \land\\
                    &\exists \iota_{\malloc,0} \ldotp \\
                    &\quad (\forall \iota' \futurestr \iota_{\malloc,0} \ldotp \forall W,i \ldotp W(i)=\iota' \Rightarrow \iota'.H (\iota'.s) (\xi^{-1}(W)) = \iota'.H (\iota'.s) (\xi^{-1}([i \mapsto W(i)])) ) \; \land \\
                    &\quad \iota_{\malloc,0}.v = \perma \; \land \\
                    &\quad (\forall \Phi \in \ExecConfs \ldotp \forall \ms_{\var{footprint}}, \hsframe \in \HeapSegments \ldotp \\
                    &\qquad \forall i, n, \size \in \nats \ldotp \forall
                    w_{\var{ret}} \in \Words \ldotp \\
                    &\qquad \quad \forall \iota_\malloc \futurestr \iota_{\malloc,0} \land \\
                    &\qquad \quad \memheap = \ms_{\var{footprint}} \uplus \hsframe \land \heapSat[\ms_{\var{footprint}}]{n}{[i \mapsto \iota_\malloc]} \land \\
                    &\qquad \quad \memreg(r_1) = \size \land \size \geq 0 \land  \memreg(r_0) = w_{\var{ret}} \land \\
                    &\qquad \quad \memreg(\pcreg) = \updatePcPerm{c_\malloc} \\ %and this needs to change with ABI.
                    &\qquad \quad \Rightarrow \\
                    &\qquad \qquad\exists \Phi' \in \ExecConfs \ldotp \exists \ms_{\var{footprint}}', \ms_{\var{alloc}} \in \HeapSegments\ldotp\\
                    &\qquad \qquad \quad \exists j \in \nats \ldotp j > 0 \land \exists b',e'\in \Addrs \ldotp \exists \iota_\malloc' \in \Regions \ldotp \\
                    &\qquad \qquad \qquad \Phi \step[j] \Phi' \land \\
                    &\qquad \qquad \qquad \memheap[\Phi']=\ms_{\var{footprint}}' \uplus \hs_{\var{alloc}} \uplus \hsframe \land\\
                    &\qquad \qquad \qquad \iota_{\malloc}' \futurewk \iota_\malloc \land \\
                    &\qquad \qquad \qquad \heapSat[\ms_{\var{footprint}}']{n-j}{[i \mapsto \iota_\malloc']} \land \\
                    &\qquad \qquad \qquad \dom(\hs_{\var{alloc}}) = [b',e'] \land \forall a \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0  \land \\
                    &\qquad \qquad \qquad \memreg[\Phi'] = \memreg[\Phi]\update{\pcreg}{\updatePcPerm{w_{\var{ret}}}}\update{r_1}{((\rwx,\glob),b',e',b')} \land \\
                    &\qquad \qquad \qquad \size - 1 = e'-b' ) \land\\
                    &\quad (\forall \Phi \in \ExecConfs \ldotp (\memreg(r_1)
                    \not\in \ints \vee \memreg(r_1) < 0) \land \memreg(\pcreg) = \updatePcPerm{c_\malloc} \Rightarrow \exists j \in \nats \ldotp \Phi \step[j] \failed)
                  \end{aligned}
                \]
              \end{specification}
              In the specification above $\iota_\malloc'$ is a future region of the initial region that governs malloc.
              \lau{What about $c_\malloc$ and the value relation? Do we add this to the specification or try to prove it based on the specification?}

@@

        \item $\npair[n'-1]{c_\adv} \in \stdvr(W)$: for $n'' < n'-1$ and $W'
          \futurestr W$ show: \\$\npair[n'']{\updatePcPerm{c_\adv}} \in
          \stder(W')$. Follows from Lemma~\ref{lem:safe-values-safe-invoke},
          together with Lemma~\ref{lem:stdvr-glob-priv-mono} and the fact that
          $c_\adv$ is non-local.  \label{f1:adv}
        \end{enumproof}

@@

\begin{align*}
  & \writeCond{} : (((\Addrs\times\Addrs) \fun\Regions) \times \Globals) \fun \Worlds \monnefun \UPred{\Addrs^2}  \\
  & \writeCond{}(\iota,\gl)(W) =  \\
  & \quad \begin{aligned}[t]
    \{ \npair{(\start,\addrend)} \mid & \;\exists r \in \var{localityReg}(g,W) \ldotp \\
    & \;\quad \exists [\start',\addrend'] \supseteq [\start,\addrend] \ldotp \\
    & \;\qquad W(r)\nsupsim[n-1] \iota_{\start',\addrend'} \text{ and }\\
    & \;\qquad W(r) \text{ is address-stratified } \}
  \end{aligned}
\end{align*}

@@

\begin{lemma}[Safe values are safe to invoke.]
  \label{lem:safe-values-safe-invoke}
  If $\npair[n+1]{w} \in \stdvr(W)$, then $\npair{\updatePcPerm{w}} \in \stder(W)$.
\end{lemma}
\begin{proof}
  \begin{enumproof}
  \item Case $w = \stdcap$ and $\start \leq \addr \leq \addrend$
    and $\perm \in \{ \exec,\rwx, \rwlx \}$:
    \begin{enumproof}
    \item $\npair[n+1]{(\perm,\start,\addrend)}\in\execCond{\gl}(W)$.\\
      By: definition of $\stdvr(W)$ using the fact that $\perm \in \{ \exec,\rwx, \rwlx \}$.
    \item $\npair[n]{((\perm,\gl),\start,\addrend,\addr)} \in \stder(W)$:
      By definition of $\execCond{}$ using the fact that $\start \leq \addr \leq \addrend$.
    \end{enumproof}
  \item Case $w = \stdcap$ and $\start \leq \addr \leq \addrend$
    and $\perm = \entry$:
    \begin{enumproof}
    \item $\npair[n+1]{(\start,\addrend,\addr)}\in\entryCond{\gl}(W)$.\\
      By: definition of $\stdvr(W)$ using the fact that $\perm = \entry$.
    \item $\npair[n]{((\exec,\gl),\start,\addrend,\addr)} \in \stder(W)$:
      By definition of $\entryCond{}$ using the fact that $\start \leq \addr \leq \addrend$.
    \item $\updatePcPerm{w} = ((\exec,\gl),\start,\addrend,\addr)$:\\
      By definition of $\updatePcPerm{\cdot}$
    \end{enumproof}
  \item Otherwise:
    $\npair{\updatePcPerm{w}} \in \stder(W)$:\\
    By Lemma~\ref{lem:failed-obs-stder}.
  \end{enumproof}
\end{proof}

\begin{lemma}[Malloc is safe to pass to adversary]
  \label{lem:malloc-in-vr}
  If $W(r) \futurestr \iota_{\malloc,0}$, then
  $\npair{c_\malloc} \in \stdvr(W)$ for all $n$.
  \item $c_\malloc = ((\entry,\glob),\base,\addrend,\addr)$.\\
    By: the malloc specification (Specification~\ref{spec:malloc}).
  \item Suffices: $\npair{(\start,\addrend,\addr)}\in\entryCond{\glob}(W)$.\\
    By definition of $\stdvr(W)$.
  \item Assume: $n' < n$, $W'\futurestr W$.\\
    Suffices: $\npair[n']{((\exec,\glob),\start,\addrend,\addr)} \in
    \stder(W')$.\\
    By: definition of the $\entryCond{}$
  \item Assume: $n''\leq n'$,
    $\npair[n'']{\reg}\in\stdrr(W')$, $\heapSat[\ms]{n''}{W'}$\\
    Suffices:
    $\npair[n'']{(\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms)}\in\observations(W')$\\
    By: definition of $\stder(W')$
  \item Assume: $i < n''$,
    $(\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms\uplus\ms_f)\step[i]
    (\halted,\mem')$\\
    Suffices: $\exists W''\futurestr W',\ms_r,\ms'\ldotp$ $\mem' =
    \ms'\uplus\ms_r\uplus\ms_f$ and $\heapSat[\ms']{n-i}{W''}$\\
    By: definition of $\observations(W')$
  \item $W'(r) \futurestr \iota_{\malloc,0}$\\
    Easy from: $W'\futurestr W$ and $W(r) \futurestr \iota_{\malloc,0}$ using
    transitivity of $\futurestr$.
  \item $\exists P : \activeReg{W'} \rightarrow \HeapSegments \ldotp$
    $\memSatPar[n'']{\ms}{W'}{P}$, i.e. $\hs = \biguplus_{r\in\activeReg{W'}}P(r)$ and
    $\forall r \in \activeReg{W'} \ldotp$ $\exists H,s \ldotp$ $W'(r) =
    (\_,s,\_,\_,H)$ and $\npair[n'']{P(r)} \in H(s)(\xi^{-1}(W'))$\\
    By: definition of $\heapSat[\ms]{n''}{W'}$.
  \item Define $\ms_{\var{frame}} = \left(\biguplus_{r'\in\activeReg{W'},r'\neq
        r}P(r')\right)\uplus\ms_f$. Then $\ms\uplus\ms_f = P(r) \uplus
    \ms_{\var{frame}}$ and $\heapSat[P(r)]{n''}{W'(r).H~(W'(r).s)~(\xi^{-1}(W'))}$.
    Easy from the previous point.
  \item $\heapSat[P(r)]{n''}{W'(r).H~(W'(r).s)~(\xi^{-1}([r\mapsto W'(r)]))}$, i.e.
    $\heapSat[P(r)]{n''}{[r\mapsto W'(r)]}$.\\
    By: the malloc specification (Specification~\ref{spec:malloc}) from the
  \item Case: $\reg(r_1) \in \ints$ and $\reg(r_1) \geq 0$
    \item Define $\var{size} = \reg(r_1)$
    \item $\exists \Phi' \in \ExecConfs, \ms_{\var{footprint}}',
      \ms_{\var{alloc}} \in \HeapSegments, j \in \nats, j > 0 \land b',e'\in
      \Addrs, \iota_\malloc' \in \Regions \ldotp$
      $(\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms\uplus\ms_f)
      \step[j] \Phi'$ and $\memheap[\Phi']=\ms_{\var{footprint}}' \uplus
      \hs_{\var{alloc}} \uplus \ms_{\var{frame}}$ and $\iota_{\malloc}'
      \futurewk W'(r)$ and $\heapSat[\ms_{\var{footprint}}']{n''-j}{[r \mapsto
        \iota_\malloc']}$ and $\dom(\hs_{\var{alloc}}) = [b',e']$ and $\forall a
      \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0$ and $\memreg[\Phi'] =
      \memreg[\Phi]\update{\pcreg}{\updatePcPerm{w_{\var{ret}}}}\update{r_1}{((\rwx,\glob),b',e',b')}$
      and $\var{size} - 1 = e'-b' )$ with $w_{\var{ret}} = \memreg(r_1)$.\\
    By: the malloc specification (Specification~\ref{spec:malloc}).
    \item Define $W'' = W'\update{r}{\iota_\malloc'}[i\mapsto
      \iota^\nwl_{b',e'}]$ for $i \not\in\dom(W')$. We have that $W''\futurewk
      [r\mapsto\iota_\malloc']$ and $W'' \futurewk W'$.\\
      By: definition of $\futurewk$ , using the fact that
      $\iota_\malloc'\futurewk W(r)$.
    \item $\npair[n''']{(\start',\addrend')}\in\readCond{\glob}(W'')$ for all $n'''$:\\
      By: definition of $\readCond{}$, using the region $W''(i)$ and Lemma~\ref{lem:nwl-subset-pwl}.
    \item $\npair[n''']{(\start',\addrend')}\in\writeCond{\iota^\nwl,\glob}(W'')$ for all $n'''$:\\
      By: definition of $\writeCond{}$, using the region $W''(i)$.
      $\npair[n''']{(p,\start',\addrend')}\in\execCond{\iota^\nwl,\glob}(W'')$
      for all $n'''$, $p \in \{\rwx,\exec\}$:\\
      By: the definition of $\execCond{}, $ the FTLR (Theorem~\ref{thm:ftlr})
      using Lemmas~\ref{lem:writecond-mono-priv}, \ref{lem:readcond-mono-priv}
      and the previous two points.
    \item $\npair[n'']{((\rwx,\glob),b',e',b')}\in\stdvr(W'')$:\\
      By: definition of $\stdvr(W'')$ and the above three points.
      $\npair[n''-j]{\memreg[\Phi]\update{r_1}{((\rwx,\glob),b',e',b')}}\in\stdrr(W'')$:\\
      By Lemma~\ref{lem:stdrr-dc}, Lemma~\ref{lem:stdrr-mono} using the fact
      that $W''\futurewk W'$ and $\npair[n'']{\memreg}\in\stdvr(W')$, together
      with the previous point.
    \item $\npair[n''']{\ms_{\var{alloc}}} \in \iota^\nwl_{b',e'}.H~
      \iota^\nwl_{b',e'}.s~ W''$ for any $n'''$:\\
      By definition of $\iota^\nwl$, $H^\nwl$ and $\stdvr(\cdot)$ and the facts
      that $\dom(\hs_{\var{alloc}}) = [b',e']$ and $\forall a
      \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0$.
    \item Define $\ms' = \left(\biguplus_{r'\in\activeReg{W'},r'\neq
          r}P(r')\right)\uplus \ms_{\var{footprint}}'\uplus\ms_{\var{alloc}}$.
      Then
      $\memheap[\Phi'] = \ms' \uplus \ms_f$ and $\heapSat[\ms']{n''-j}{W''}$:\\
      By the facts that $\memheap[\Phi']=\ms_{\var{footprint}}' \uplus
      \hs_{\var{alloc}} \uplus \ms_{\var{frame}}$, $\ms_{\var{frame}} =
      \left(\biguplus_{r'\in\activeReg{W'},r'\neq r}P(r')\right)\uplus\ms_f$,
      the previous point, the facts that
      $\heapSat[\ms_{\var{footprint}}']{n''-j}{[r \mapsto \iota_\malloc']}$ and
      $W''\futurewk [r\mapsto\iota_\malloc']$, the facts that ($\forall r \in
      \activeReg{W'} \ldotp$ $\exists H,s \ldotp$ $W'(r) =, (\_,s,\_,\_,H)$ and
      $\npair[n'']{P(r)} \in H(s)(\xi^{-1}(W'))$) and $W'' \futurewk W'$ and the
      public monotonicity and downwards closedness of all islands, and finally
      the definition of $W''$.
    \item $\npair[n''-j+1]{w_{\var{ret}}} \in \stdvr(W'')$:\\
      By Lemma~\ref{lem:stdvr-mono-wk}, the fact that $W''\futurewk W'$,
      Lemma~\ref{lem:stdvr-dc}, and teh fact that
      $\npair[n'']{w_{\var{ret}}}\in\stdvr(W')$, which follows from
      $w_{\var{ret}} = \memreg(r_1)$ and $\npair[n'']{\reg}\in\stdrr(W')$.
    \item $\npair[n''-j]{\updatePcPerm{w_{\var{ret}}}} \in \stder(W'')$:\\
      By Lemma~\ref{lem:safe-values-safe-invoke} from the previous point.
      $\npair[n''-j]{(\memreg[\Phi]\update{r_1}{((\rwx,\glob),b',e',b')}\update{\pcreg}{\updatePcPerm{w_{\var{ret}}}},
        \ms')} \in \observations(W'')$:\\
      By: definition of $\stder(W'')$, using the previous point and the facts
      that
      $\npair[n''-j]{\memreg[\Phi]\update{r_1}{((\rwx,\glob),b',e',b')}}\in\stdrr(W'')$,
      $\heapSat[\ms']{n''-j}{W''}$
    \item $i > j$ and $\Phi'\step[i-j]
      (\halted,\mem')$.\\
      By combining
      $(\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms\uplus\ms_f)\step[i]
      (\halted,\mem')$ with
      $(\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms\uplus\ms_f)
      \step[j] \Phi'$ using Lemma~\label{lem:determinacy}.
    \item $\exists W''' \futurestr W'', \hs_r, \hs'' \ldotp$ $\heap' = \hs'' \uplus \hs_r \uplus \ms_f$ and $\heapSat[\hs'']{n-i}{W'''}$.\\
      By: definition of $\observations(W''')$ from the two previous points.
    \item $W''' \futurestr W'$: \\
      By Lemma~\ref{lem:future-priv-pub-trans}, using the previous point and the fact that $W'' \futurewk
      W'$.
  \item Case: $\reg(r_1)\not\in\ints \vee \reg(r_1) < 0$
    \item $\exists j\ldotp (\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms\uplus\ms_f)\step[j]
      \failed$\\
      By: the malloc specification (Specification~\ref{spec:malloc}).
    \item Contradiction with 
      $(\reg\update{\pcreg}{((\exec,\glob),\start,\addrend,\addr)},\ms\uplus\ms_f)\step[i]
      (\halted,\mem')$

@@

\begin{lemma}[Transitivity proberties between private and public future worlds]
  \label{lem:future-priv-pub-trans}
\[
  W'' \futurestr W' \land W' \futurewk W \Rightarrow W'' \futurestr W
\]
and
\[
  W'' \futurewk W' \land W' \futurestr W \Rightarrow W'' \futurestr W
\]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:future-priv-pub-trans}]
  % TODO
\end{proof}

@@

\subsubsection{Value relation}
\begin{lemma}[Value relation downwards closed]
  \label{lem:stdvr-dc}
  \[
    n' \leq n \land \npair{w} \in \stdvr(W) \Rightarrow \npair[n']{w} \in \stdvr(W)
  \]
\end{lemma}
\begin{proof}
  By definition of $\stdvr(W)$ using Lemma~\ref{lem:readcond-dc},
  \ref{lem:writecond-dc}, \ref{lem:execcond-dc} and \ref{lem:entrycond-dc}.
\end{proof}

\begin{lemma}[Register relation downwards closed]
  \label{lem:stdrr-dc}
  \[
    n' \leq n \land \npair{w} \in \stdrr(W) \Rightarrow \npair[n']{w} \in \stdrr(W)
  \]
\end{lemma}
\begin{proof}
  By definition of $\stdrr(W)$ using Lemma~\ref{stdvr-dc}.
\end{proof}

\begin{lemma}[Value relation monotone wrt $\futurewk$]
  \label{lem:stdvr-mono-wk}
  \[
    W' \futurewk W \land \npair{w} \in \stdvr(W) \Rightarrow \npair{w} \in \stdvr(W')
  \]
\end{lemma}
\begin{proof}[Proof of lemma~\ref{lem:stdvr-mono-wk}]
  Follows from Lemma~\ref{lem:readcond-mono-pub}, Lemma~\ref{lem:writecond-mono-pub}, Lemma~\ref{lem:execcond-mono-pub}, and Lemma~\ref{lem:entrycond-mono-pub}.
\end{proof}
